---
title: "WT1_mutation_prognosis_analysis"
author: "Yabin Liu"
date: "2020/8/12"
output: html_document
---

```{r}
source("~/lyb_proj_20200717/lyb_function.R")
```

##Part I: validation of WT1 MUT vs WT DEGs
###01.count matrx & clinical data input
```{r}
aml_all_count.matrix <- read.table("/mnt5/BEAT_AML_RNAseq_count/06.count_merge_new/AML_merge.count2.txt",row.names = 1,header = TRUE)
aml_all_tpm.matrix <- read.table("/mnt5/BEAT_AML_RNAseq_count/06.count_merge_new/AML_merge.count2.tpm.txt",row.names = 1,header = TRUE,stringsAsFactors = FALSE)
aml_all_wt1.tpm <- read.table("/mnt5/BEAT_AML_RNAseq_count/06.count_merge_new/AML_RNAseq.wt1.anno2.txt",header = TRUE,sep="\t",stringsAsFactors = FALSE)
#aml_all_wt1.tpm$WT1_tpm <- aml_all_wt1.tpm$WT1_br2
aml_all_wt1.clinc <- read.table("/mnt5/BEAT_AML_RNAseq_count/06.count_merge_new/AML_combind_clinical.process.txt",header = TRUE,sep="\t",stringsAsFactors = FALSE)
aml_all_wt1.clinc<-merge(aml_all_wt1.tpm,aml_all_wt1.clinc, by.x=2,by.y=1, all=FALSE)
aml_all_wt1.clinc <- data.table::as.data.table(aml_all_wt1.clinc)
aml_all_wt1.clinc[,`:=`(IDH2 = IDH2_p140 + IDH2_p172)]
```

```{r}
tmp.df<-aml_all_wt1.tpm %>% filter(Type == "Normal")
normal.list <- tmp.df$SampleID
index <- match(normal.list, colnames(aml_all_tpm.matrix))
aml_all_tpm.matrix.nm <- aml_all_tpm.matrix[,c(1:3,index)]
```


```{r}
aml_all_wt1.tpm$Source2 <- factor(aml_all_wt1.tpm$Source2, levels=c("BEAT","TARGET","TCGA","CD2017","CD34","MNC"))

ggplot(aml_all_wt1.tpm,aes(x=Source2,y=log2(WT1_tpm),color=Source2)) + geom_boxplot(outlier.shape = NA,show.legend = FALSE) + geom_jitter(size=0.5,show.legend = FALSE) + theme(panel.border = element_rect(fill=NA,linetype = 1),panel.background = element_blank()) + scale_color_manual(values = c(brewer.pal(4,"Paired"),"grey50","black"))
```

```{r}
a <- aml_all_wt1.clinc 
#%>%  filter(Source.x == "BEAT")
#a <- a[a$isDNAseq=="yes",]
a <- a[! duplicated(a$PatientId),]
as.data.frame(table(apply(X = a[, c("FLT3_ITD", "NPM1", "DNMT3A","normal"), drop = FALSE], 1, paste, collapse = "")))
```


###02.Extract BEAT AML and Goupping by WT1 status
```{r}
aml_design_primary <- aml_all_wt1.clinc %>%  filter(Source.x == "BEAT" & Type == "Primary")
aml_design_primary <- aml_design_primary[aml_design_primary$isDNAseq == "yes",]
aml_design_primary <- aml_design_primary[! duplicated(aml_design_primary$PatientId),]

upper<-quantile(aml_design_primary[aml_design_primary$WT1 != 1,]$WT1_tpm)[4]
lower<-quantile(aml_design_primary[aml_design_primary$WT1 != 1,]$WT1_tpm)[2]
aml_design_primary$Group <- "WME"
aml_design_primary[aml_design_primary$WT1_tpm > as.numeric(upper),]$Group <- "WHE"
aml_design_primary[aml_design_primary$WT1_tpm <= as.numeric(lower),]$Group <- "WLE"
aml_design_primary[aml_design_primary$WT1 == 1,]$Group <- "MUT"
aml_design_primary <- data.frame(SampleID=aml_design_primary$SampleID,WT1_tpm=aml_design_primary$WT1_tpm,Group=aml_design_primary$Group,Time=aml_design_primary$overallSurvival,Status=aml_design_primary$vitalStatus)
tmp.df<-aml_all_wt1.tpm %>% filter(Type == "Normal")
tmp.df <- data.frame(SampleID=tmp.df$SampleID,WT1_tpm=tmp.df$WT1_tpm,Group=rep("Normal",nrow(tmp.df)),Time=rep(NA,nrow(tmp.df)),Status=rep(NA,nrow(tmp.df)))
aml_design_primary <- rbind(aml_design_primary,tmp.df)

aml_design_primary %>% group_by(Group) %>% summarise(mean=mean(WT1_tpm),var=var(WT1_tpm),max=max(WT1_tpm),min=min(WT1_tpm),num=n())
```
```{r}
aml_design_primary$Group <- factor(aml_design_primary$Group, levels=c("MUT","WHE","WME","WLE","Normal"))

ggplot(aml_design_primary,aes(x=Group,y=log2(WT1_tpm),color=Group)) + geom_boxplot(outlier.shape = NA,show.legend = FALSE) + geom_jitter(size=0.5,show.legend = FALSE) + theme(panel.border = element_rect(fill=NA,linetype = 1),panel.background = element_blank()) + scale_color_manual(values = c(brewer.pal(4,"Set1"),"grey50"))
```

###04.DEGs of AML vs Normal: DESeq2
```{r}
#exculed_features.list <- c("TET2", "ASXL1", "IDH1", "IDH2_p140", "IDH2_p172", "EZH2")
exculed_features.list <- c("WT1","TET2", "IDH1", "IDH2_p140", "IDH2_p172")
#index <- match(exculed_features.list, colnames(aml_all_wt1.clinc))
ls_chr<-lapply(exculed_features.list, function(x){
#  aml_all_wt1.clinc[aml_all_wt1.clinc[,x] == 1,]$SampleID
  aml_all_wt1.clinc[.(1), on = x, SampleID]
})
exculed_sample.list<-unique(do.call(c,ls_chr))
```

```{r}
#aml_design.nm<-aml_design_primary[! aml_design_primary$SampleID %in% exculed_sample.list,]
aml_design.nm<-aml_design_primary
aml_design.nm$Group <- as.character(aml_design.nm$Group)
aml_design.nm[aml_design.nm$Group != "Normal",]$Group <- "AML"
aml_design.nm$Group <- factor(aml_design.nm$Group,levels=c("Normal","AML"))
aml_design.nm %>% group_by(Group) %>% summarise(n())
```

```{r}
aml_count.nm <- aml_all_count.matrix[,as.character(aml_design.nm$SampleID)]
AML_NM.deg <- DESeq2_DEG_analysis(aml_count.nm, aml_design.nm)
AML_NM.deg <- DESeq2_DEG_extract(AML_NM.deg, aml_design.nm, plot=FALSE)
AML_NM.deg.list <- c(AML_NM.deg$up$Row.names,AML_NM.deg$down$Row.names)
```

###05.Design of MUT vs WT(MUT group: WT1 TET2 IDH1 IHD2)

```{r}
#aml_design.mut <- aml_design_primary %>% filter(Group == "WHE" | Group == "WME")
aml_design.mut <- aml_design_primary %>% filter(Group != "Normal" )
#aml_design.mut<-aml_design.mut[! aml_design.mut$SampleID %in% exculed_sample.list,]
#aml_design.mut<-rbind(aml_design.mut,aml_design_primary[aml_design_primary$Group=="MUT",])
#aml_design.mut %>% group_by(Group) %>% summarise(n())
aml_design.mut$Group <- as.character(aml_design.mut$Group)
#aml_design.mut[aml_design.mut$Group == "WHE",]$Group <- "WT"
#aml_design.mut[aml_design.mut$Group == "WME",]$Group <- "WT"
aml_design.mut$Group <- "WT"
aml_design.mut[aml_design.mut$SampleID %in% exculed_sample.list,]$Group <- "MUT"
aml_design.mut$Group <- factor(aml_design.mut$Group,levels=c("WT","MUT"))
rownames(aml_design.mut) <- as.character(aml_design.mut$SampleID)
aml_design.mut <- aml_design.mut %>% arrange(Group,WT1_tpm)
aml_design.mut %>% group_by(Group) %>% summarise(n())

```

```{r}
aml_count.mut <- aml_all_count.matrix[,as.character(aml_design.mut$SampleID)]
WT1_MUT.deg <- DESeq2_DEG_analysis(aml_count.mut, aml_design.mut)
WT1_MUT.deg <- DESeq2_DEG_extract(WT1_MUT.deg, aml_design.mut,plot=TRUE)
```

##Part II: Gene Enrichment Analysis of DEGS

```{r}
WT1_MUT.deg$up$Entrez <- TransGeneID(WT1_MUT.deg$up$Symbol, "Symbol", "Entrez", organism = "hsa")
WT1_MUT.deg$down$Entrez <- TransGeneID(WT1_MUT.deg$down$Symbol, "Symbol", "Entrez", organism = "hsa")
```

```{r}
deg.list <- c(na.omit(WT1_MUT.deg$up$Entrez),na.omit(WT1_MUT.deg$down$Entrez))
```

```{r}
Enricher <- enrich_combind(deg.list,0.5,0.5)
```

```{r}
enricher_plot(Enricher,1:5,1:5,1:5,1:5,1:5,5) + ggtitle("WT1 Mut vs WT DEGs")
```

##Part III: WGCNA analysis of DEGs

###01.Select  the optimum β value
```{r}
wt1_mut.deg.list<-c(WT1_MUT.deg$up$Row.names,WT1_MUT.deg$down$Row.names)
sample.list <- as.character(aml_design.mut$SampleID)
wt1_mut.deg.tpm <- aml_all_tpm.matrix[wt1_mut.deg.list,sample.list]
datExpr <- t(wt1_mut.deg.tpm)
#sample.list <- as.character(aml_design.nm[aml_design.nm$Group=="AML",]$SampleID)
#aml_nm.deg.tpm <- aml_all_tpm.matrix[AML_NM.deg.list,sample.list]
#datExpr <- t(aml_nm.deg.tpm)
powers = c(c(1:10), seq(from = 12, to=30, by=2))
powers = c(1:12)
sft = pickSoftThreshold(datExpr, powerVector = powers, verbose = 5)
```

```{r}
  # Plot the results:
  ##sizeGrWindow(9, 5)
  par(mfrow = c(1,2));
  cex1 = 0.9;
  # Scale-free topology fit index as a function of the soft-thresholding power
  plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
       xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
       main = paste("Scale independence"));
  text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
       labels=powers,cex=cex1,col="red");
  # this line corresponds to using an R^2 cut-off of h
  abline(h=0.90,col="red")
  # Mean connectivity as a function of the soft-thresholding power
  plot(sft$fitIndices[,1], sft$fitIndices[,5],
       xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
       main = paste("Mean connectivity"))
  text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
```

###02.Contruct the co-expression net
```{r}
net = blockwiseModules(
                 datExpr,
                 power = sft$powerEstimate,
                 maxBlockSize = 6000,
                 TOMType = "unsigned", minModuleSize = 30,
                 reassignThreshold = 0, mergeCutHeight = 0.25,
                 numericLabels = TRUE, pamRespectsDendro = FALSE,
                 saveTOMs = TRUE,
                 saveTOMFileBase = "AS-green-FPKM-TOM",
                 verbose = 3
 )
 table(net$colors)
```

```{r}
# Convert labels to colors for plotting
mergedColors = labels2colors(net$colors)
table(mergedColors)
# Plot the dendrogram and the module colors underneath
plotDendroAndColors(net$dendrograms[[1]], mergedColors[net$blockGenes[[1]]],
                    "Module colors",
                    dendroLabels = FALSE, hang = 0.03,
                    addGuide = TRUE, guideHang = 0.05)
## assign all of the gene to their corresponding module 
## hclust for the genes.
```

###03.Corr analysis of module and clinc trait 
```{r}
row_index<-match(sample.list,aml_all_wt1.clinc$SampleID)
cow_index<-c("ageAtDiagnosis","WT1","WT1_tpm","Sex","vitalStatus","overallSurvival","ELN2017_Myclass")
datTraits <- aml_all_wt1.clinc[row_index,cow_index,with=FALSE]
datTraits <- as.data.frame(datTraits)
#design<-as.data.frame(model.matrix(~0+ datTraits$ELN2017_Myclass))
#colnames(design) <- c("Adverse","Favorable","Intermediate")
#datTraits<-cbind(datTraits,design)
#datTraits<-subset(datTraits,select=-ELN2017_Myclass)
rownames(datTraits) <- sample.list
datTraits$overallSurvival <- as.numeric(datTraits$overallSurvival)/365
datTraits[datTraits$vitalStatus == "Death",]$vitalStatus <- 1
datTraits[datTraits$vitalStatus == "Alive",]$vitalStatus <- 0
datTraits[datTraits$Sex == "Male",]$Sex <- 1
datTraits[datTraits$Sex == "Female",]$Sex <- 0 
datTraits[datTraits$ELN2017_Myclass == "Favorable",]$ELN2017_Myclass <- 0
datTraits[datTraits$ELN2017_Myclass == "Intermediate",]$ELN2017_Myclass <- 1
datTraits[datTraits$ELN2017_Myclass == "Adverse",]$ELN2017_Myclass <- 2

nGenes = ncol(datExpr)
nSamples = nrow(datExpr)

  moduleColors <- labels2colors(net$colors)
  # Recalculate MEs with color labels
  MEs0 = moduleEigengenes(datExpr, moduleColors)$eigengenes
  MEs = orderMEs(MEs0); ##不同颜色的模块的ME值矩阵(样本vs模块)
  moduleTraitCor = cor(MEs, datTraits , use = "p");
  moduleTraitPvalue = corPvalueStudent(moduleTraitCor, nSamples)
  
  sizeGrWindow(12,8)
  # Will display correlations and their p-values
  textMatrix = paste(signif(moduleTraitCor, 2), "\n(",
                     signif(moduleTraitPvalue, 1), ")", sep = "");
  dim(textMatrix) = dim(moduleTraitCor)
  par(mar = c(6, 8.5, 3, 3));
  # Display the correlation values within a heatmap plot
  labeledHeatmap(Matrix = moduleTraitCor,
                 xLabels = colnames(datTraits),
                 yLabels = names(MEs),
                 ySymbols = names(MEs),
                 colorLabels = FALSE,
                 colors = greenWhiteRed(50),
                 textMatrix = textMatrix,
                 setStdMargins = FALSE,
                 cex.text = 0.5,
                 zlim = c(-1,1),
                 main = paste("Module-trait relationships"))
```

###03.Analysis of genes in the interested Module
```{r}
moduleTraitPvalue <- as.data.frame(moduleTraitPvalue)
moduleTraitPvalue %>% filter(overallSurvival < 0.05)
moduleTraitCor[rownames(moduleTraitPvalue %>% filter(overallSurvival < 0.05)),]
```
```{r}
modNames = substring(names(MEs), 3)
geneModuleMembership = as.data.frame(cor(datExpr, MEs, use = "p"))
MMPvalue = as.data.frame(corPvalueStudent(as.matrix(geneModuleMembership), nSamples))
names(geneModuleMembership) = paste("MM", modNames, sep="")
names(MMPvalue) = paste("p.MM", modNames, sep="")
```
```{r}
geneTraitSignificance = as.data.frame(cor(datExpr, datTraits, use = "p"));
GSPvalue = as.data.frame(corPvalueStudent(as.matrix(geneTraitSignificance), nSamples));
names(geneTraitSignificance) = paste("GS.", names(datTraits), sep="");
names(GSPvalue) = paste("p.GS.", names(datTraits), sep="");
```

```{r}
module <- "black"
trait <- "WT1"
column <- match(module, modNames);
column2 <- match(trait, colnames(datTraits))
moduleGenes <- moduleColors==module;
sizeGrWindow(7, 7);
par(mfrow = c(1,1));
verboseScatterplot(abs(geneModuleMembership[moduleGenes, column]),
                   abs(geneTraitSignificance[moduleGenes, column2]),
                   xlab = paste("Module Membership in", module, "module"),
                   ylab = paste("Gene significance for", trait  , "trait"),
                   main = paste("Module membership vs. gene significance\n"),
                   cex.main = 1.2, cex.lab = 1.2, cex.axis = 1.2, col = module)
```

###04. Relation of module and trait
```{r}
geneTree <- net$dendrograms[[1]]; 
dissTOM <- 1-TOMsimilarityFromExpr(datExpr, power = sft$powerEstimate); 
plotTOM <- dissTOM^10; 
diag(plotTOM) <- NA; 
TOMplot(plotTOM, geneTree, moduleColors, main = "Network heatmap plot, all genes")
```

```{r}
MET = orderMEs(cbind(MEs0, datTraits))
# Plot the relationships among the eigengenes and the trait
  sizeGrWindow(5,7.5);
  par(cex = 0.9)
  plotEigengeneNetworks(MET, "", marDendro = c(0,4,1,2), marHeatmap = c(3,4,1,2), cex.lab = 0.8, xLabelsAngle
                        = 90)
  # Plot the dendrogram
  sizeGrWindow(6,6);
  par(cex = 1.0)
  ## 模块的聚类图
  plotEigengeneNetworks(MET, "Eigengene dendrogram", marDendro = c(0,4,2,0),
                        plotHeatmaps = FALSE)
  # Plot the heatmap matrix (note: this plot will overwrite the dendrogram plot)
  par(cex = 1.0)
  ## 性状与模块热图
  plotEigengeneNetworks(MET, "Eigengene adjacency heatmap", marHeatmap = c(3,4,2,2),
                        plotDendrograms = FALSE, xLabelsAngle = 90)
```

###05.Extract genes in the interested module 
```{r}
module = c("black","red","brown")
genes = colnames(datExpr) 
inModule = (moduleColors %in% module);
#inModule2 = (moduleColors=="magenta");
modGenes = genes[inModule];
#modGenes2 = genes[inModule2];
#modGenes <- c(modGenes,modGenes2)
gene_id_anno <- read.table("/mnt5/BEAT_AML_RNAseq_count/03.merge_and_combat/gene_id_trans.txt", header = TRUE, sep = "\t",stringsAsFactors=FALSE,row.names = 1)
index <- match(modGenes,rownames(gene_id_anno))
degs.wgcna.df<-gene_id_anno[index,]
degs.wgcna.df <- degs.wgcna.df %>% filter(Type == "protein_coding" | Type == "lincRNA")
```

```{r}
risk_gene.list <- degs.wgcna.df$Symbol
TOM = TOMsimilarityFromExpr(datExpr, power = sft$powerEstimate)
modTOM = TOM[inModule, inModule]
dimnames(modTOM) = list(gene_id_anno[index,]$Symbol, gene_id_anno[index,]$Symbol)
index2 <-match(risk_gene.list,gene_id_anno[index,]$Symbol)
modTOM_sig <- modTOM[index2,index2] 

cyt = exportNetworkToCytoscape(
  modTOM_sig,
  edgeFile = paste("CytoscapeInput-edges-", paste(module, collapse="-"), ".txt", sep=""),
  nodeFile = paste("CytoscapeInput-nodes-", paste(module, collapse="-"), ".txt", sep=""),
  weighted = TRUE,
  threshold = 0.0,
  nodeNames = risk_gene.list
#  nodeAttr = moduleColors[inModule]
)
```

##Part IV: Lasso-Cox Regression Analysis and Calc the risk score

###01. extract tmp & merge clinc
```{r}
col_index <- match(as.character(aml_design.mut$SampleID),colnames(aml_all_tpm.matrix))
row_index <- match(rownames(degs.wgcna.df), rownames(aml_all_tpm.matrix))
degs.wgcna.tpm <- aml_all_tpm.matrix[row_index,col_index]
rownames(degs.wgcna.tpm) <- aml_all_tpm.matrix$Symbol[row_index]
degs.wgcna.tpm <- t(degs.wgcna.tpm)
df.cox <- merge(degs.wgcna.tpm, aml_all_wt1.clinc, by.x=0,by.y =2, all=FALSE)
df.cox[df.cox$vitalStatus  == "Death",]$vitalStatus <- 1
df.cox[df.cox$vitalStatus  == "Alive",]$vitalStatus <- 0
df.cox$vitalStatus <- as.numeric(df.cox$vitalStatus)
df.cox$overallSurvival <- as.numeric(df.cox$overallSurvival)
df.cox <- df.cox %>% filter(overallSurvival > 0)
df.cox %>% group_by(vitalStatus) %>% summarise(n())
```

### 02.Multivariate Cox Regression Analysis
```{r}
survobj <- Surv(df.cox$overallSurvival,df.cox$vitalStatus)
survpre <- as.matrix(df.cox[,degs.wgcna.df$Symbol])

model <- coxph( survobj ~ survpre)
a<-summary(model)
a<-a$coefficients
risk_gene.list <-gsub("survpre","",rownames(a[a[,5] < 0.01 & a[,2] <=10 & a[,2] >=0.1,]))
#a[a[,5] < 0.05,]
feature_interest.list <- c("WT1","TET2","IDH1","IDH2","ageAtDiagnosis")

survpre_mut <- df.cox[,feature_interest.list,drop=FALSE]
#survpre_mut$age <- as.numeric(survpre_mut$age)
survpre_mut$ageAtDiagnosis <- as.numeric(survpre_mut$ageAtDiagnosis)
survpre_sig <- df.cox[,risk_gene.list]
survpre_os <-  df.cox[,c("overallSurvival","vitalStatus")]
colnames(survpre_os) <- c("Time","Status")
surv_model.df <- cbind(survpre_sig,survpre_mut)
surv_model.df <- as.data.frame(row.names = df.cox$Row.names, cbind(surv_model.df,survpre_os))
surv_model.df <- na.omit(surv_model.df)

survobj <- Surv(surv_model.df$Time,surv_model.df$Status)
survpre <- as.matrix(surv_model.df[,c(risk_gene.list,feature_interest.list)])
model <- coxph( survobj ~ survpre)
hr.cox.sum <-summary(model)
hr.cox <- as.data.frame(cbind(hr.cox.sum$coefficients, hr.cox.sum$conf.int))
hr.cox$Feature <- gsub("survpre","",rownames(hr.cox))
hr.cox <- data.table::as.data.table(hr.cox[,c(10,1,5,6,8,9)])
colnames(hr.cox) <- c("Feature","Coefficient","Pvalue","Hazard.ratio","HR.Lower.95","HR.Upper.95")

#model <-  coxph( Surv(Time, Status) ~  SP140 + GZMA + PM20D1 + PIGR + PYHIN1 + DNAI2 + CYP4F22 + ZNF683 + PRF1 + AC109826.1 + WT1 + TET2 + IDH1 + IDH2 + ageAtDiagnosis, data = surv_model.df)
#ggforest(model)

#a<-predict(model,type="lp")
#b<-rs.df.clinc$Risk_score
#c<-cbind(a,b)
```

###03. risk score and plot

```{r}
ls_df <- lapply(1:nrow(surv_model.df), function(x){
    sample <- rownames(surv_model.df)[x]
    score <-sum(sapply(1:nrow(hr.cox),function(i){
      coef = hr.cox$Coefficient[i]
      tpm = surv_model.df[x,colnames(surv_model.df) == hr.cox$Feature[i]]
      coef * tpm
    }))
    data.frame(Sample = sample, Risk_score=score)
  })
rs.df <- do.call(rbind, ls_df)
rs.df$RS_norm<-sapply(1:nrow(rs.df),function(i){
    (rs.df$Risk_score[i] - mean(rs.df$Risk_score))/sd(rs.df$Risk_score)
})
rs.df$Risk_Group <- "High_risk"
rs.df[rs.df$RS_norm < median(rs.df$RS_norm),]$Risk_Group <- "Low_risk"
rs.df$Sample <- gsub("\\.","-",rs.df$Sample)
rownames(surv_model.df) <- gsub("\\.","-",rownames(surv_model.df))
rs.df.clinc <- merge(rs.df,surv_model.df, by.x = 1, by.y =0, all = FALSE)
rs.df.clinc <- merge(rs.df.clinc, aml_all_wt1.clinc, by.x = 1, by.y =2, all = FALSE)
```


```{r}
#rs.df.clinc[rs.df.clinc$Time > 10*365,]$Time <- 10*365
model <- coxph( Surv(Time, Status) ~ Risk_score, data = rs.df.clinc)
summary(model)
ggforest(model)
fit <- survfit(Surv(Time/365, Status) ~ Risk_Group, data= rs.df.clinc)
ggsurvplot(fit,palette = c("#FF7F00","#1F78B4"),risk.table = TRUE,ncensor.plot=FALSE,pval=TRUE,conf.int = FALSE,xlab="Time in years")
plot_survial_risk(rs.df.clinc)
plot_roc_curve(rs.df.clinc)
```

04.Univariate Cox Regression Analysis
```{r}
ls_df <- lapply(2:(ncol(degs.wgcna.tpm)+1), function(i){
    pretty_aml <- data.frame(time   = df.cox$overallSurvival, 
                             status = df.cox$vitalStatus, 
                             TPM    = df.cox[,i])
    Gene_label <- colnames(df.cox)[i]
    model <- coxph( Surv(time, status) ~ TPM, data = pretty_aml)
    cox_result <- summary(model)
    data.frame(row.names = Gene_label, cox_result$conf.int,PV=cox_result$coefficients[5])
})

hr <- do.call(rbind, ls_df)
rm(ls_df)
hr$rank <- rank(hr$PV,ties.method="first")
hr <- hr %>% dplyr::arrange(rank)
#row.names(hr) <- gsub("\\.","-",row.names(hr))
dim(hr[hr$PV <0.05 & hr$exp.coef.<=10 & hr$exp.coef. >=0.1,])
```


###05. Lasso-cox model select genes 
```{r}
#a<-hr[match(risk_gene.list,rownames(hr)),]
  
library(glmnet)
#a <- df.cox[,match(risk_gene.list,colnames(df.cox))]
a <- df.cox[,match(rownames(hr[hr$PV <0.05 & hr$exp.coef.<=10 & hr$exp.coef. >=0.1,]),colnames(df.cox))]
#a <- df.cox[,match(degs.wgcna.df$Symbol,colnames(df.cox))]
#a <- a[,! colnames(a) %in% exculed_features.list]
rownames(a)<-df.cox$Row.names
b <- data.frame(time=df.cox$overallSurvival, status=df.cox$vitalStatus)
rownames(b)<-df.cox$Row.names
a <- as.matrix(a)
b <- as.matrix(b)
fit <- glmnet(a,b,family="cox")
plot(fit)
set.seed(40)
cvfit <- cv.glmnet(a,b,family="cox")
plot(cvfit)
cvfit.min <- as.data.frame(as.matrix(coef(cvfit, s = "lambda.min")))
cvfit.min$Feature <- row.names(cvfit.min)
colnames(cvfit.min) <- c("Weight", "Feature")
cvfit.min <- cvfit.min[order(abs(cvfit.min$Weight), decreasing = T),]
feature.gene <- cvfit.min[which(cvfit.min$Weight != 0),]$Feature
```

```{r}
gg<-hr[match(feature.gene, rownames(hr)),]
colnames(gg) <- c("HR","HR2","lower_HR","upper_HR", "Pvalue", "Rank")
gg$Symbols <- as.factor(rownames(gg))

ggplot(gg,aes(x=HR,y=Symbols))  + 
  geom_point(shape=18,size=1,aes(color=-log10(Pvalue))) + 
  blank + 
  geom_vline(xintercept = 1,linetype="dotted") + 
  geom_pointrange(aes(xmin=lower_HR,xmax=upper_HR,color=-log10(Pvalue)),shape=18)+ylab("") + 
  scale_colour_gradient(low = brewer.pal(9,"Greens")[5], high = brewer.pal(9,"Greens")[9]) +
  theme(panel.border = element_rect(fill = NA, linetype = 1, size = 1), axis.line = element_blank()) +
  theme(legend.position = c(0.95,0.95), legend.justification = c("right", "top"), legend.title = element_text()) + scale_x_log10()
```

```{r}
library(forestplot)
gg <- hr[match(feature.gene, rownames(hr)),]
gg.text <- data.frame( V1=c("Gene",rownames(gg)), V2=c("HR",round(gg$exp.coef., 2)))
forestplot(labeltext=gg.text,
           mean = c( NA, gg$exp.coef. ),
           lower = c(NA, gg$lower..95 ),
           upper = c(NA, gg$upper..95),
           xlab="Hazard Ratio",
           hrzl_lines=list("1" = gpar(lwd=2, col="black"), "2" = gpar(lwd=2, col="black"),"17" = gpar(lwd=2, col="black"))
           )
```


###06.Validation 
```{r}
aml_all_wt1.clinc.v2 <- aml_all_wt1.clinc
for (x in c(27:29,32:33,37:38,41:42,44:57,92)){
  colnames(aml_all_wt1.clinc.v2)[x] <-  paste0(colnames(aml_all_wt1.clinc.v2)[x],".m")
}

aml_all_wt1.clinc.rm <- aml_all_wt1.clinc %>%  filter(isDNAseq == "yes")
aml_all_wt1.clinc.rm <- aml_all_wt1.clinc.rm[! duplicated(aml_all_wt1.clinc.rm$PatientId),]
feature_sig.list <- c("WT1","TET2","IDH1","IDH2","ageAtDiagnosis")
#feature_sig.list <- c("WT1.m","TET2.m","IDH1.m","IDH2.m","ageAtDiagnosis")
#gene_sig.list <- risk_gene.list
gene_sig.list <- c(feature.gene)
#gene_sig.list <- corr_neg
```

####BEAT
```{r}
sample.list <- aml_all_wt1.clinc.rm[aml_all_wt1.clinc.rm$Source.x == "BEAT" & aml_all_wt1.clinc.rm$Type == "Primary",]$SampleID
rs.df.clinc.beat <- RiskScore_multivar_cox(sample.list, gene_sig.list, feature_sig.list, aml_all_tpm.matrix, aml_all_wt1.clinc)
hr.cox.beat <- rs.df.clinc.beat$HR
rs.df.clinc.beat <- rs.df.clinc.beat$Clinc
model <- coxph( Surv(Time, Status) ~ Risk_score, data = rs.df.clinc.beat)
summary(model)
ggforest(model)
fit <- survfit(Surv(Time/365, Status) ~ Risk_Group, data= rs.df.clinc.beat)
ggsurvplot(fit,palette = c("#FF7F00","#1F78B4"),risk.table = TRUE,ncensor.plot=FALSE,pval=TRUE,conf.int = FALSE,xlab="Time in years")
plot_survial_risk(rs.df.clinc.beat)
plot_roc_curve(rs.df.clinc.beat)
```



####TCGA
```{r}
sample.list <- aml_all_wt1.clinc.rm[aml_all_wt1.clinc.rm$Source.x == "TCGA",]$SampleID
rs.df.clinc.tcga <- RiskScore_multivar_cox(sample.list, gene_sig.list, feature_sig.list, aml_all_tpm.matrix, aml_all_wt1.clinc)
hr.cox.tcga <- rs.df.clinc.tcga$HR
rs.df.clinc.tcga <- rs.df.clinc.tcga$Clinc
model <- coxph( Surv(Time, Status) ~ Risk_score, data = rs.df.clinc.tcga)
summary(model)
ggforest(model)
fit <- survfit(Surv(Time/365, Status) ~ Risk_Group, data= rs.df.clinc.tcga)
ggsurvplot(fit,palette = c("#FF7F00","#1F78B4"),risk.table = TRUE,ncensor.plot=FALSE,pval=TRUE,conf.int = FALSE,xlab="Time in years")
plot_survial_risk(rs.df.clinc.tcga)
plot_roc_curve(rs.df.clinc.tcga)
```


####TARGET
```{r}
sample.list <- aml_all_wt1.clinc.rm[aml_all_wt1.clinc.rm$Source.x == "TARGET",]$SampleID
rs.df.clinc.target <- RiskScore_multivar_cox(sample.list, gene_sig.list, feature_sig.list, aml_all_tpm.matrix, aml_all_wt1.clinc)
hr.cox.target <- rs.df.clinc.target$HR
rs.df.clinc.target <- rs.df.clinc.target$Clinc
rs.df.clinc.target[rs.df.clinc.target$Risk_score < -2,]$Risk_score = -2

model <- coxph( Surv(Time, Status) ~ Risk_score, data = rs.df.clinc.target)
summary(model)
ggforest(model)
fit <- survfit(Surv(Time/365, Status) ~ Risk_Group, data= rs.df.clinc.target)
ggsurvplot(fit,palette = c("#FF7F00","#1F78B4"),risk.table = TRUE,ncensor.plot=FALSE,pval=TRUE,conf.int = FALSE,xlab="Time in years")
plot_survial_risk(rs.df.clinc.target)
plot_roc_curve(rs.df.clinc.target)
```

####ALL
```{r}
#sample.list <- aml_all_wt1.clinc.rm$SampleID
sample.list <- aml_all_wt1.clinc.rm[aml_all_wt1.clinc.rm$Source.x != "TARGET" & aml_all_wt1.clinc.rm$Type == "Primary",]$SampleID
rs.df.clinc.all <- RiskScore_multivar_cox(sample.list,gene_sig.list, feature_sig.list,aml_all_tpm.matrix, aml_all_wt1.clinc)
hr.cox.all <- rs.df.clinc.all$HR
rs.df.clinc.all <- rs.df.clinc.all$Clinc
model <- coxph( Surv(Time, Status) ~ Risk_score, data = rs.df.clinc.all)
summary(model)
ggforest(model)
fit <- survfit(Surv(Time/365, Status) ~ Risk_Group, data= rs.df.clinc.all)
ggsurvplot(fit,palette = c("#FF7F00","#1F78B4"),risk.table = TRUE,ncensor.plot=FALSE,pval=TRUE,conf.int = FALSE,xlab="Time in years")
plot_survial_risk(rs.df.clinc.all)
plot_roc_curve(rs.df.clinc.all)
```


##Part V: Methylation correlation of WT1-TET2-IDH1/2 Genes

###01.Target gene TPM extract
```{r}
col_index <- match(as.character(aml_design.mut$SampleID),colnames(aml_all_tpm.matrix))
row_index <- match(rownames(degs.wgcna.df), rownames(aml_all_tpm.matrix))
degs.wgcna.tpm <- aml_all_tpm.matrix[row_index,col_index]
rownames(degs.wgcna.tpm) <- aml_all_tpm.matrix$Symbol[row_index]
degs.wgcna.tpm <- t(degs.wgcna.tpm)

WT1_status.target_gene.tpm<-aml_all_tpm.matrix[match(feature.gene,aml_all_tpm.matrix$Symbol),]
WT1_status.target_gene.tpm.t <- t(WT1_status.target_gene.tpm)
WT1_status.target_gene.tpm.t<-WT1_status.target_gene.tpm.t[c(1,4:nrow(WT1_status.target_gene.tpm.t)),]
rownames(WT1_status.target_gene.tpm.t)<-gsub("\\.","-",rownames(WT1_status.target_gene.tpm.t))
write.table(WT1_status.target_gene.tpm.t,"/mnt5/BEAT_AML_RNAseq_count/05.TPM_merge_clinical/AML_TPM_WT1.surv_target.tpm.txt",quote = FALSE, sep="\t",row.names = TRUE)
```

###02.process METH and TPM matrix of WT1-status target genes
```{bash}
cd  /mnt5/BEAT_AML_RNAseq_count/05.TPM_merge_clinical/
sh work.sh
```

```{bash}
cd /mnt5/TCGA_LAML_Methylation/04.corr_TPM_METH_of_Target_Gene/
bash work.sh
```

```{r}
corr_tpm.matrix <- read.table("/mnt5/TCGA_LAML_Methylation/04.corr_TPM_METH_of_Target_Gene/target.gene.TSS.3k.METH450K_probe.TPM.corr.matrix",quote = "", sep="\t", header = TRUE, row.names = 1, stringsAsFactors = FALSE)
corr_meth.matrix <- read.table("/mnt5/TCGA_LAML_Methylation/04.corr_TPM_METH_of_Target_Gene/target.gene.TSS.3k.METH450K_probe.METH.corr.matrix", quote = "", sep="\t", header = TRUE, row.names = 1, stringsAsFactors = FALSE)
```

```{r}
ls_df <- lapply(1:nrow(corr_tpm.matrix), function(i){
    result.corr<-cor.test(as.numeric(corr_tpm.matrix[i,]), as.numeric(corr_meth.matrix[i,]), method = "pearson")
    mean_meth <- mean(as.numeric(corr_meth.matrix[i,]))
    mean_tpm <- mean(as.numeric(corr_tpm.matrix[i,]))
    var_meth <- var(as.numeric(corr_meth.matrix[i,]))
    var_tpm <- var(as.numeric(corr_tpm.matrix[i,]))
    max_meth <- max(as.numeric(corr_meth.matrix[i,]))
    min_meth <- min(as.numeric(corr_meth.matrix[i,]))
    max_tpm <- max(as.numeric(corr_tpm.matrix[i,]))
    min_tpm <- min(as.numeric(corr_tpm.matrix[i,]))
    gene.prob <-  row.names(corr_tpm.matrix[i,])
    data.frame(row.names = gene.prob, Corr=result.corr$estimate, PV=result.corr$p.value,
               Mean_Meth = mean_meth, Var_Meth = var_meth,
               Max_meth  = max_meth,  Min_Meth = min_meth, 
               Mean_TPM  = mean_tpm,  Var_TPM  = var_tpm,
               Max_TPM   = max_tpm,   Min_TPM  = min_tpm)
})

corr <- do.call(rbind, ls_df)
rm(ls_df)

gene.prob.df <- as.data.frame(strsplit(row.names(corr),","),stringsAsFactors=FALSE)
corr$Gene <- as.character(gene.prob.df[1,])
corr$Prob <- as.character(gene.prob.df[2,])

#a<-corr[corr$PV < 0.05 & corr$Corr < 0,]$Gene
#a[! duplicated(a)]
corr_neg<-unique(corr[corr$PV < 0.05 & corr$Corr < 0,]$Gene)
corr_pos<-unique(corr[corr$PV < 0.05 & corr$Corr > 0,]$Gene)
corr_sig <- unique(corr[corr$PV < 0.05,]$Gene)
```


###03.Meth prob  corr plot of WT1-TET2-IDH1/2 survial-related deg
```{r}
#gg <- corr
#gg <- corr[corr$Gene %in%  rownames(hr.lasso),]
#gg <- corr[corr$Gene %in%  corr_sig,]
gg <- corr[corr$Gene %in%  corr_neg,]
gg[gg$PV < 0.001,]$PV = 0.001


ggplot(gg,aes(y=reorder(Gene,Corr),x=Corr,color=-log10(PV))) + geom_boxplot() + geom_jitter() + blank + geom_vline(xintercept = 0, linetype= 2)+ scale_colour_gradient(low = brewer.pal(9,"BuPu")[4], high = brewer.pal(9,"BuPu")[9])+ theme(panel.border = element_rect(linetype = 1, size = 1, fill = NA), axis.line = element_blank())

ggplot(gg,aes(y=reorder(Prob,Corr),x=Corr,color=-log10(PV), fill=-log10(PV))) + 
  geom_point(shape = 21) + 
  facet_wrap(~ Gene, scales="free",ncol=4) + 
  blank + 
  geom_vline(xintercept = 0, linetype= 2) + 
  theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()) + 
  scale_colour_gradient(name = "-log10(Pvalue)",low = brewer.pal(9,"BuPu")[4], high = brewer.pal(9,"BuPu")[9]) +
  scale_fill_gradient(name = "-log10(Pvalue)",low = brewer.pal(9,"BuPu")[4], high = brewer.pal(9,"BuPu")[9])  +
  ylab("Probes located in the promoter region of each gene") +
  xlab("Pearson's correlation coefficient")
#  theme(legend.position = c(1,0.00), legend.justification = c("right","bottom"), legend.background = element_rect(fill = NA))
```

###04.Volcano plot of WT1-TET2-IDH1/2 survial-related deg
```{r}
AML_NM.deg.list <- c(AML_NM.deg$up$Symbol,AML_NM.deg$down$Symbol,feature.gene)
#hr.vol.plot <- volcano_plot_Deseq2(WT1_MUT.deg$result,WT1_MUT.deg$result$Symbol,feature.gene)
hr.vol.plot <- volcano_plot_Deseq2(WT1_MUT.deg$result,AML_NM.deg.list,feature.gene)
hr.vol.plot + ylim(0, 15) + xlim(-4,4)
```

###05. Boxplot of WT1-TET2-IDH1/2 sig deg
```{r}
boxplot.list.beat <- lapply(gene_sig.list, function(x){
  expression_boxplot_byMut(x, rs.df.clinc.beat, aml_all_tpm.matrix.nm)
})
plot_grid(plotlist = boxplot.list.beat, nrow = 2)

boxplot.list.tcga <- lapply(gene_sig.list, function(x){
  expression_boxplot_byMut(x, rs.df.clinc.tcga, aml_all_tpm.matrix.nm)
})
plot_grid(plotlist = boxplot.list.tcga, nrow = 2)

boxplot.list.target <- lapply(gene_sig.list, function(x){
  expression_boxplot_byMut(x, rs.df.clinc.target, aml_all_tpm.matrix.nm)
})
plot_grid(plotlist = boxplot.list.target, nrow = 2)

boxplot.list.all <- lapply(gene_sig.list, function(x){
  expression_boxplot_byMut(x, rs.df.clinc.all, aml_all_tpm.matrix.nm)
})
plot_grid(plotlist = boxplot.list.all, nrow = 2)
```

##Part VI: Cibersort
```{r}
rs.df.clinc.beat.tpm <- aml_all_tpm.matrix[aml_all_tpm.matrix$Type == "protein_coding",c(1,match(rs.df.clinc.beat$Sample,colnames(aml_all_tpm.matrix)))]
rs.df.clinc.beat.tpm <- rs.df.clinc.beat.tpm[! duplicated(rs.df.clinc.beat.tpm$Symbol) ,]
write.table(rs.df.clinc.beat.tpm, "/data/liuyabin/lyb_proj_20200717/rs.df.clinc.beat.tpm.txt", row.names = FALSE, quote = FALSE, sep = "\t")
```


```{r}
#save.image(file="/data/liuyabin/lyb_proj_20200717/WT1_mut_pg.RData")
#load("/data/liuyabin/lyb_proj_20200717/WT1_mut_pg.RData")
```
